Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-02-24 manuscript/ms.tex
Minor edit to Introduction
Added timing and model_counts tables

\usepackage{amsmath}
\usepackage{amssymb}
\pdfoutput=1
\usepackage[pdftex]{graphicx}
%\usepackage[mathbf,mathcal]{euler}
%\usepackage{citesort}
\usepackage{dcolumn}
\usepackage{boxedminipage}
\usepackage{verbatim}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}

@@

Proteins play a diverse variety of roles in biology, and the understanding of their function---and how mutations can cause dysfunction and disease---is the preoccupation of much of modern biology. 
The diminishing cost of nucleic acid sequencing technologies has produced an enormous wealth of sequence data, yielding a large collection of protein-coding open reading frames that provide basic information about these proteins (at the level of primary amino acid sequences) for numerous organisms [CITE]. 
Complementing this, large-scale structural biology efforts such as the Protein Structure Initiative (PSI) and Structural Genomics Consortium (SGC) have yielded a great number of protein structures, allowing comparative modeling to provide insight into the static structures many of these proteins adopt [CITE review of structural biology efforts or current comparative modeling?].
% TODO Maybe it is not necessary to mention comparative modeling here? If so, this could be changed to:
% Complementing this, large-scale structural biology efforts such as the Protein Structure Initiative (PSI) and Structural Genomics Consortium (SGC) have provided insight into the static structures which these proteins can adopt [CITE review of structural biology efforts?].

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\pdfoutput=1
\usepackage[pdftex]{graphicx}
%\usepackage[mathbf,mathcal]{euler}
%\usepackage{citesort}
\usepackage{dcolumn}
\usepackage{boxedminipage}
\usepackage{verbatim}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage[group-separator={,}]{siunitx}

@@

Proteins play a diverse variety of roles in biology, and the understanding of their function---and how mutations can cause dysfunction and disease---is the preoccupation of much of modern biology. 
The diminishing cost of nucleic acid sequencing technologies has produced an enormous wealth of sequence data, yielding a large collection of protein-coding open reading frames that provide basic information about these proteins (at the level of primary amino acid sequences) for numerous organisms [CITE]. 
Complementing this, large-scale structural biology efforts such as the Protein Structure Initiative (PSI) and Structural Genomics Consortium (SGC) have yielded a great number of protein structures, allowing comparative modeling to provide insight into the static structures many of these proteins adopt [CITE review of structural biology efforts or current comparative modeling?].
% TODO Maybe it is not necessary to mention comparative modeling here? The structures themselves provide insight. If so, this could be changed to:
% Complementing this, large-scale structural biology efforts such as the Protein Structure Initiative (PSI) and Structural Genomics Consortium (SGC) have provided insight into the static structures which these proteins can adopt [CITE review of structural biology efforts?].

@@

\begin{table}
\begin{tabular}{l|c|c|c}

    & SRC & ABL & All 90 TKs \\
    \hline
    Templates & \num{4433} & \num{4433} & \num{398970} \\
    Models & \num{4248} & \num{4250} & \num{382568} \\
    Unique models & \num{4093} & \num{4247} & \num{378839} \\
    Refined models & \num{4023} & \num{4241} & \num{373513} \\

\end{tabular}
\label{tab:model_counts}
\caption{Model counts}
\end{table}

\begin{table}
\begin{tabular}{l|c}

    & Average timings per template/model (h:m:s) \\
    \hline
    Template reconstruction & 03:00:00 \\
    Modeling & 00:01:19 \\
    Refinement (100 ps implicit solvent MD) & 00:01:58 \\

\end{tabular}
\label{tab:timings}
\caption{Pipeline timings for 90 TKs}
\end{table}
